### 2018-04-12 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Tidied to work with all linux systems
FP2 Notes Update

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - FP2}

@@

@@

\frac{d^2y}{dx^2}+y=0

@@

$$\frac{d^2y}{dx^2}=\frac{d}{du}\Bigg(e^u\frac{dy}{dx}\Bigg)$$

@@

$$\frac{d^2y}{dx^2}-\frac{dy}{du}+\frac{dy}{du}+y=0$$

@@

$$\frac{d^2y}{dx^2}+y=0$$

@@

>>>>

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - FP2}

@@

\usepackage{chngcntr} %Resets equation numbering after each section or subsection
\counterwithin*{equation}{section}
\counterwithin*{equation}{subsection}

@@

\frac{d^2y}{du^2}+y=0

@@

$$\frac{d^2y}{du^2}=\frac{d}{du}\Bigg(e^u\frac{dy}{dx}\Bigg)$$

@@

$$\frac{d^2y}{du^2}-\frac{dy}{du}+\frac{dy}{du}+y=0$$

@@

$$\frac{d^2y}{du^2}+y=0$$

@@

\subsection{Example 2}
\textit{Show that the transformation $x=e^u$ transforms the differential equation}
\begin{equation}\label{eq2:1}
x^2\frac{d^2y}{dx^2}-7x\frac{dy}{dx}+16y=2\ln x, \ x>0
into the differential equation
\begin{equation}\label{eq2:2}
\frac{d^2y}{du^2}-8\frac{dy}{du}+16y=2u
\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
$$
\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
\textcolor{red}{Substitute the values into the original formula, replacing $x$ with $e^u$}
$$e^{2u}\times e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)-7e^u\times e^{-u}\frac{dy}{du}+16y=2u$$
$$-\frac{dy}{du}+\frac{d^2y}{du^2}-7\frac{dy}{du}+16y=2u$$
$$\frac{d^2y}{du^2}-8\frac{dy}{du}+16y=2u$$
